NEXTY: A CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER BLOCKCHAIN

### 2019-05-21 Paper.tex
update technical paper

\section{How to authorize an account to become a block sealer}\label{sec:authorize}
The system will set up a configuration parameter to determine the minimum value, $min-ntf$, that an account need to have to become block sealer. Nexty will build and develop a smart contract, which allow {\small NTF} token holder, having enough token, to grant another account called ``executing-account'' to become the block sealer by setting ``authorized-sealer'' state in the smart contract with the value equal to address of {\small NTF} holder. If an address already has an ``authorized-sealer'' value, it can not receive authorization from another NTF holder until the NTF holder has made the withdrawal it from ``authorized-sealer''. The ``authorized-sealer'' list will be determined at the check point block of each sealing round by reading state from the smart contract at that point of time. If in the current sealing round, any ``authorized-sealer'' does not perform at least one sealing activity, the ``authorized-sealer'' value will be withdrawn to its {\small NTF} holder by updating the state of the smart contract at the checkpoint block number of the next sealing round and of course that ``authorized-sealer'' will not be involved in the next sealing rounds until it will be authorized to become ``authorized-sealer'' again.

\section{Block sealing mechanism}\label{sec:sealing}
The {\small DCCS} block sealing mechanism will be implemented  as in following steps. Firstly, the sealers will be numbered from $0$ to $n - 1$ (called ``sealing-id'') randomly at the beginning of each sealing round; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the smart contract at the \textit{checkpoint block number} of the corresponding sealing round. To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new sealing round.

@@

\begin{description}
\item[block] is the first block number, a.k.a  \textit{checkpoint block number} of the sealing round.
\item[$\Lambda_{\mathrm{k}}$] is the address that the {\small NTF} holder has set as ``authorized-sealer'' in the smart contract.
\item[\texttt{\small KEC}] is the \textbf{\small {SHA-3 Keccak-512}} hash function of any input.
\end{description}

@@

To ensure performance of the system, the ``sealing-id'' of the all authorized sealers will be snapshot only once from the smart contract state at the \textit{checkpoint block number} of each sealing round and stored in the local database as well as in \textbf{lru cache} of each node.

\subsection{Scenario 1}\label{ch:scenario_1} If sealing node is not in recent sealers. The node will determine whether it's the in-turn sealer for the next block or not, according to the following formula:

@@

\begin{description}
\item[$\nu$] is the current block number that is being sealed.
\item[block] is the first block number, a.k.a \textit{checkpoint block number}, of the current sealing round.
\item[$\Pi$] total number of authorized sealer reading from smart contract state at the \textit{checkpoint block} of the current sealing round.
\end{description}

If the remainder $\sigma_{\mathrm{k}}$ equal to ``sealing-id'' of the node, then that node has the right to seal block immediately. Otherwise, at each of the next block, sealing nodes have to wait a course of time, $\psi_{\mathrm{k}}$, which is calculated by the formula:

\begin{eqnarray}
\alpha = 001.387978000 \\
\beta = 000.002313279 \\
\gamma = 000.004626590 \\
\delta = 199.999400000
\end{eqnarray}

@@

\subsection{Scenario 2}\label{ch:scenario_2} If sealing node is in recent sealers

In this scenario, sealers still can continue to seal block, but they have to wait a period of time longer than all other sealers, not in recent sealers. This is procedure to ensure that the system can still generate blocks, even when there is only one sealer, but the chain be suspended for a very long time. The waiting time ranges from $3$ - $30$ minutes, if there are $1,000$ - $10,000$ authorized sealers and only one or few active sealers.

Waiting time, $\psi_{\mathrm{k}}$,  is caculated by the following formula:

\begin{eqnarray}
\alpha = 001.387978000 \\
\beta = 000.002313279 \\
\gamma = 000.004626590 \\
\delta = 199.999400000
\end{eqnarray}

\begin{multline}\label{eq:psi_2}
\psi_{\mathrm{k}} \equiv \sum_{i=1}^{n} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta) \\ 
+ \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
\end{multline}

The coefficients of the above formula are assumed as following. The sealing node having ``sealing-id'' equal to $\sigma_{\mathrm{k}}$, calculated by formula $\eqref{eq:sigma}$, will have the priority to seal block before 400ms, the next sealing node will have the priority to seal block before 350ms, then 320ms,... till the final sealing node with approximately to 200ms. Its graph corresponds to the function $\texttt{\small y} = \frac{a} {(b * x + c)} + \texttt{\small d}$

To estimate values for the parameters, we use curve fitting method to find relatives coefficient in the website \href{https://mycurvefit.com/}{My Curve Fit} with the variance \footnote{R² is 1 minus the ratio of sum of the squares of the residuals divided by the sum of the squares of the differences between Y fit and the mean Y value} $\approx 1$.
\\
\\
\includegraphics[width=0.48\textwidth, height=4cm]{curve-fit}
\\
A sealing round of all authorized sealer is called an epoch. Epoch will have various length, depends on the number of sealers in a chain of each sealing round.

A sealer who is worried about being withdrawn authorized sealer to {\small NTF} holder might not participate in sealing activity in a sealing round, but still occupies the right to seal block at some point earlier than his/her sealing turn; causes welter and racing for sealing block. By calculating the fixed waiting time for each sealer, using formula $\eqref{eq:psi}$ or $\eqref{eq:psi_2}$, consensus are able to keep track of sealer. Nexty blockchain will verify a block, sealed by an ``authorized-sealer'', by figuring out if the generating time of ``authorized-sealer''’s block is smaller than it's waiting time.

@@

After each sealing round, reward value $\Re$ of each sealer will be calculated as the minimum value of the total reward divided by the active sealers according to the proportion of {\small NTF} they have on the total {\small NTF} of the sealers who participated in the seal.

\begin{eqnarray}
\theta = \frac{\Omega}{N} \\
\phi = \frac{\Upsilon_{NTF}}{\Xi_{NTF}}
\end{eqnarray}

\begin{equation}\label{eq:re}
\Re \equiv \min(\theta, \phi)
\end{equation}

\begin{description}
\item[$\Omega$] total reward
\item[N] total number of active sealer of the current sealing round
\item[$\Upsilon_{NTF}$] amount of NTF token that the owner of active sealer is holding
\item[$\Xi_{NTF}$] total amount of NTF token that all active sealer are holding
\end{description}

According to formula $\eqref{eq:re}$, people who own {\small NTF} in a natural way will divide his/her {\small NTF} into many wallets in order to equip multiple sealers, instead of building only one sealer and spend too much  {\small NTF} on it. This ensures the Nexty chain will have sufficiently large number of nodes to make Nexty chain become highly decentralization, stability and robust.

Total reward $\Omega$ is the amount of {\small NTF} was produced after each sealing round, calculated as \textit{[reward generated in one block]} * \textit{[number of blocks generated in that sealing round]}.

The number of rewards generated for a block is equal to the number of rewards per year divided by $\mathbf{15,768,000}$, the expected number of block within one year (initial configuration of block time is 2 seconds).

The amount of rewards in a year is calculated in the following proportions:

\begin{center}
  \begin{tabular}{@{} cc @{}}
    \hline
    Year &  \% of circulating supply \\ 
    \hline
    1 & 10 \\ 
    2 & 5 \\ 
    3 & 2 \\ 
    4 & 1 \\ 
    5 & 1 \\     
    ... & ... \\ 
    ... & ... \\ 
    ... & ... \\ 
    n &  1 \\
    \hline
  \end{tabular}
\end{center}

>>>>

\section{How to authorize an account to become a block sealer}\label{sec:authorize}
The system will set up a configuration parameter to define the minimum value, $\mathbf{50,000}$ {\small NTF}, that an account need to deposit into Nexty governance smart contract to become a block sealer. Nexty will build and develop a governance smart contract, which allow {\small NTF} token holder, having enough token, to grant another account called ``executing-account'' to become the block sealer by setting ``authorized-sealer'' state in the smart contract with the value equal to address of {\small NTF} holder. If an address already has an ``authorized-sealer'' value, it can not receive authorization from another NTF holder until the NTF holder has made the withdrawal it from ``authorized-sealer''. The ``authorized-sealer'' list will be determined at the check point block of each epoch by reading canonical state from the smart contract at that point of time. If in the current epoch, any ``authorized-sealer'' does not perform at least one sealing activity, the ``authorized-sealer'' value will be withdrawn to its {\small NTF} holder by updating the state of the smart contract at the checkpoint block number of the next epoch and of course that ``authorized-sealer'' will not be involved in the next epoch until it will be authorized to become ``authorized-sealer'' again. We will introduce more detail about this on Nexty governance section later \ref{sec:governace}.

\section{Block sealing mechanism}\label{sec:sealing}
The {\small DCCS} block sealing mechanism will be implemented  as in following steps. Firstly, the sealers will be numbered from $0$ to $n - 1$ (called ``sealing-id'') randomly at the beginning of each epoch; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the governance smart contract at the canonical chain from \textit{checkpoint block number} of the corresponding epoch. To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new epoch.

@@

\begin{description}
\item[block] is the canonical block number from the \textit{checkpoint block number} of the epoch. a.k.a \textit{checkpoint block number} - 7
\item[$\Lambda_{\mathrm{k}}$] is the address that the {\small NTF} holder has set as ``authorized-sealer'' in the governance smart contract.
\item[\texttt{\small KEC}] is the \textbf{\small {SHA-3 Keccak-512}} hash function of any input.
\end{description}

@@

To ensure performance of the system, the ``sealing-id'' of the all authorized sealers will be snapshot only once from the smart contract state at the canonical chain from \textit{checkpoint block number} of each epoch and stored in the local database as well as in \textbf{lru cache} of each node.

If sealing node is not in recent sealers. The node will determine whether it's the in-turn sealer for the next block or not, according to the following formula:

@@

\begin{description}
\item[$\nu$] is the current block number that is being sealed.
\item[block] is the canonical block number from \textit{checkpoint block number}, of the current epoch.
\item[$\Pi$] total number of authorized sealer reading from smart contract state at the canonical block from \textit{checkpoint block} of the current epoch.
\end{description}

If the remainder $\sigma_{\mathrm{k}}$ equal to ``sealing-id'' of the node, then that node has in-turn sealer and seal block immediately with highest \textit{difficulty}. Otherwise, nodes will wait a period of time, $\psi_{\mathrm{k}}$, which is calculated by the formula:

\begin{eqnarray}
\alpha = 001.387978000 \\
\beta = 000.002313279 \\
\gamma = 000.004626590 \\
\delta = 499.999400000
\end{eqnarray}

@@

The coefficients of the above formula are assumed as following. The sealing node having ``sealing-id'' equal to $\sigma_{\mathrm{k}}$, calculated by formula $\eqref{eq:sigma}$, will have the priority to seal block before 400ms, the next sealing node will have the priority to seal block before 850ms, then 820ms,... till the final sealing node with approximately to 500ms. Its graph corresponds to the function $\texttt{\small y} = \frac{a} {(b * x + c)} + \texttt{\small d}$

To estimate values for the parameters, we use curve fitting method to find relatives coefficient in the website \href{https://mycurvefit.com/}{My Curve Fit} with the variance \footnote{R² is 1 minus the ratio of sum of the squares of the residuals divided by the sum of the squares of the differences between Y fit and the mean Y value} $\approx 1$.
\\
\\
\includegraphics[width=0.48\textwidth, height=4cm]{curve-fit}
\\

The difficulty of sealing block for \textit{n} sealers will be calculated in the formula \eqref{eq:difficulty} as below

\begin{equation}\label{eq:difficulty}
    d(i) \equiv
    \begin{cases}
    	n	& \quad \text{if } sealer \text{ is in-turn}\\
	n - k_i & \quad \text{if } sealer \text{ is out-turn}
    \end{cases}
\end{equation}

${k_i}$ is the relative position of \textit{out-turn} sealer ${i^{th}}$ to the position of \textit{in-turn} sealer in the current sealing order list.

\section{Nexty Governance}\label{sec:governace}

This section will describe detail implementation of registration smart contract deployed at address \textbf{0x12345} using for consensus system.

\subsection{Terminology}

\begin{description}
\item[sealer] a participant in the Nexty consensus system. You can become one by depositing {\small DEPOSIT\_SIZE} {\small NTFs} into the Nexty mechanism.
\item[active sealer set] those sealer who are currently participating, and which the Nexty mechanism looks to seal blocks and other consensus objects.
\item[withdrawal period] number of epochs between a sealer exit and the sealer balance being withdraw-able.
\item[coinbase] the account address that sealer will use to sign when sealing block.
\item[registration contract] a smart contract for handling Nexty consensus mechanism.
\end{description}

\subsection{Constants}

\begin{center}
  \begin{tabular}{{l|l|l}}
    \hline
    Constant & Value & Unit \\
    \hline
    BLOCK\_TIME & ${2}$ & seconds \\
    EPOCH\_LENGTH & ${3,000}$ & blocks \\
    DEPOSIT\_SIZE & ${50,000}$ & {\small NTFs} \\
    WITHDRAWAL\_PERIOD & ${30,000}$ & blocks \\
    \hline
  \end{tabular}
\end{center}

\subsection{Sealer status codes}

\begin{description}
\item[PENDING\_ACTIVE = 0] Sealer deposited enough {\small NTFs} into registration contract successfully. 
\item[ACTIVE = 1] Sealer send request to become a sealer and added into activation sealer set successfully.
\item[PENDING\_WITHDRAW = 2] Sealer send request to exit from activation sealer set successfully. Sealer casted out of activation sealer set.
\item[WITHDRAWN = 3] Sealer already withdrawn their deposit {\small NTFs} successfully. They can only make withdrawal after withdrawal period.
\item[PENALIZED = 127] Sealer marked as penalized node (update by consensus or voting result via dapp) and cannot become active sealer and cannot withdraw balance neither.
\end{description}

\subsection{Nexty chain registration contract}
A registration contract is added to the Nexty chain to deposit {\small NTF} and activation sealer set management. It has some below basic functions:

\subsubsection{Sealer Operations}
\begin{description}
\item[Deposit] Transfer the {\small NTF} from token holder to registration contract. Sealer might have to approve contract to transfer an amount of {\small NTF} before calling this function.
\item[Join] To allow deposited {\small NTF} participate joining in as sealer. Participate already must deposit enough {\small NTF} via \textbf{Deposit} function. it takes \textbf{coinbase} as parameter.
\item[Exit] Request to exit out of activation sealer set.	
\item[Withdraw] To withdraw sealer’s {\small NTF} balance when they already exited and after \textbf{withdrawal period}.
\end{description}

\subsubsection{Sealer Record}
\begin{description}
\item[Coinbase address] sealer’s coinbase address to sign when sealing block
\item[Balance] the total amount of {\small NTF} that sealer has deposited
\item[Status] Sealer status code
\item[Requested Block Number] The block number at which sealer send request to exit out of activation sealer set.
\end{description}

\subsection{How to become a sealer}
\begin{enumerate}
\item A participant should deposit at least {\small DEPOSIT\_SIZE} {\small NTFs} into registration contract, a.k.a the network have maximum ~200 candidate nodes can become a sealer. Sealer status will be set to {\small PENDING\_ACTIVE}.
\item A participant need to set their \textbf{coinbase} to seal the block and receive reward on their equivalent {\small NTF} token holder address.
\item A participant call registration contract method to become sealer. Sealer status be updated to {\small ACTIVE}.
\item At next checkpoint of the epoch, sealer request be cast and the sealer be added into consensus \textbf{activation sealer set}.
\end{enumerate}

\subsection{How to exit from activation sealer and NTF withdrawal}
\begin{enumerate}
\item Sealer call registration contract method to request for exiting from activation sealer set and sealer status be updated to {\small PENDING\_WITHDRAW} but still in the activation sealer set on the current epoch.
\item At next checkpoint of the epoch, sealer exit request be cast and the sealer be removed out of \textbf{activation sealer set}. 
\item Sealer can call register contract method to withdrawn their deposited {\small NTF} after a withdrawal period. The sealer status be changed to {\small WITHDRAWN} after sealer withdraw the {\small NTFs} successfully.
\end{enumerate}

\subsection{Sealer authorization}
When a node starting with --${mine}$ option then they need to unlock the unique \textbf{coinbase} account setting in the activation sealer set. If the \textbf{coinbase} was not found in the current epoch \textbf{activation sealer set} then unauthorization error will be throw and it cannot start mining but they still can continue to sync block preparing for sealing later.

@@

Reward will be added immediately into sealer’s account balance after sealing a block. The reward for a block is equal to the number of rewards per year divided by $\mathbf{15,768,000}$, the expected number of block within one year (initial configuration of block time is 2 seconds). The amount of rewards of each block sealing in a specific year is calculated in the following proportions:

\begin{center}
  \begin{tabular}{c | l | l}
    \hline
    Year &  \% of total supply & Reward/Blk\\ 
    \hline
    1 & 10.000 & 1,141\\ 
    2 & 5.000 & 627 \\ 
    3 & 2.500 & 329 \\ 
    4 & 1.250 & 169 \\ 
    5 & 0.625 & 85 \\
    6 & 0.500 & 69 \\
    ... & 0.500 & ... \\
    ... & 0.500 & ... \\ 
    n & 0.500 & ... \\
    \hline
  \end{tabular}
\end{center}
